Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/intro.tex
BGP Path Guide -> BGP-SAS
Changed breakthrough to chokepoint in intro

We developed a
suite of tools, called \toolname{}, for studying national chokepoints on
the AS graph efficiently. To illustrate these ideas and tools, we
study how national chokepoint potential correlates with two independent
measures of civil liberty, finding that a significant relationship exists between national chokepoint potential and each measure.
The paper extends earlier research on AS topology in several ways: it introduces chokepoint potential, it presents open-source cross-platform tools and datasetes for simulating Border Gateway Protocol (BGP) paths,
determining national chokepoint potential, and analyzing changes over time.  In addition, we report and analyze data for several countries of interest.
%Our measure of border ASes, chokepoint potential, defined in detail
%in section 3, is a succinct way to estimate the important properties of
%border ASes related to the ability of a nation to censor and surveil, and our aggregate extension of this measure to
%the national level, national breakthrough potential, is an effective way to evaluate and
%compare nations and analyze the evolution of the AS-level censorship and surveillance landscape.\Ben[inline]{This paragraph seems a little redundant now. It is a combo of other previous writing, but I am not sure what to cut.}

@@

% Rest of Paper Layout
\par
The layout of the rest of this paper is as follows: Section 2 provides relavent background information
to the problems we are investigating; Section 3 introduces and defines the measures of chokepoint
potential and national breakthrough potential; Section 4 details our tool for simulating and evaluating 
AS topologies \toolname{}; Section 5
explains our experimental setups; Sections 6, 7, and 8 provide results, discussion, and related work
respectively.

>>>>

We developed a
suite of tools, called BGP Simulation Analysis and Storage (\toolname{}), for studying national 
chokepoints on
the AS graph efficiently. To illustrate these ideas and tools, we
study how national chokepoint potential correlates with two independent
measures of civil liberty, finding that a significant relationship exists between national chokepoint potential and each measure.
The paper extends earlier research on AS topology in several ways: it introduces chokepoint potential, it presents open-source cross-platform tools and datasetes for simulating Border Gateway Protocol (BGP) paths,
determining national chokepoint potential, and analyzing changes over time.  In addition, we report and analyze data for several countries of interest.
%Our measure of border ASes, chokepoint potential, defined in detail
%in section 3, is a succinct way to estimate the important properties of
%border ASes related to the ability of a nation to censor and surveil, and our aggregate extension of this measure to
%the national level, national breakthrough potential, is an effective way to evaluate and
%compare nations and analyze the evolution of the AS-level censorship and surveillance landscape.\Ben[inline]{This paragraph seems a little redundant now. It is a combo of other previous writing, but I am not sure what to cut.}

@@

% Rest of Paper Layout
\par
The layout of the rest of this paper is as follows: Section 2 provides relavent background information
to the problems we are investigating; Section 3 introduces and defines the measures of chokepoint
potential and national chokepoint potential; Section 4 details our tool for simulating and evaluating 
AS topologies \toolname{}; Section 5
explains our experimental setups; Sections 6, 7, and 8 provide results, discussion, and related work
respectively.
